### 2020-12-12 Thesis-Chapter4-Tools.tex
Editorial improvements

Argument mapping tools originated in 1970 with text-based \acp{IBIS} designed to break down \acp{wicked-prob} and
document the reasoned approaches that go into solving them \cite{kunz_issues_1970}. Interest in \acp{IBIS} has waxed and
waned. Some software tools have been developed, including the now-defunct gIBIS \cite{conklin_gibis_1988} and Compendium
\cite{dutoit_hypermedia_2006}, which were designed to produce graphical argument representations. Argdown is a recent
tool that generates graphical \acp{argmap} from structures specified in a Markdown-based language
\cite{voigt_argdown_2018}. Argdown is used in \mychap{chap-arguments} to analyze the arguments used in the \ac{EA}
debate.

@@

\begin{figure}[h]
    \centering\CaptionFontSize
    \includegraphics[width=0.85\linewidth]{dfds/build/dfd-key.png}
    \caption{Expanded set of DFD symbols}
    \label{fig-dfd-key}
\end{figure}

>>>>

% TODO: can probably cut more
Argument mapping tools originated in 1970 with text-based \acp{IBIS} \cite{kunz_issues_1970}. Interest in \acp{IBIS} has
waxed and waned. Some software tools have been developed, including the now-defunct gIBIS \cite{conklin_gibis_1988} and
Compendium \cite{dutoit_hypermedia_2006}, which were designed to produce graphical argument representations. Argdown is
a recent tool that generates graphical \acp{argmap} from structures specified in a Markdown-based language
\cite{voigt_argdown_2018}. Argdown is used in \mychap{chap-arguments} to analyze the arguments used in the \ac{EA}
debate.

@@

\begin{figure}[t]
    \centering\CaptionFontSize
    \includegraphics[width=0.85\linewidth]{dfds/build/dfd-key.png}
    \caption{Expanded set of DFD symbols}
    \label{fig-dfd-key}
\end{figure}

### 2020-12-12 Thesis-Chapter5-Arguments.tex
Editorial improvements

This chapter will analyze the \ac{encryption} debate using \acp{argmap}. The maps facilitate comprehension of the
debate, but there are two important shortcomings of the maps presented here. First, argument maps should be used simply
as tools in the collaborative pursuit of the problem definition and solution. One can approximate the debate based on
research, but it is not a replacement for debate arising from live discussion. Second, \acp{argmap} may deceptively
portray the strength of an argument. Argument nodes do not indicate their strength or validity. If ten unsound arguments
were presented against one indisputable argument, the side with more arguments would, regardless of their integrity,
appear stronger. With those qualifications in mind, let us begin by examining the factors at the center of the conflict.

@@

\Acl{LE}, argues that encryption handcuffs its investigational capacity. The \ac{FBI} brands strong encryption as
``warrant-proof'' and states that ``the government often cannot obtain the electronic evidence necessary to investigate
and prosecute threats to public and national safety'' \cite{fbi_2020}. The pro-\ac{EA} argument is typically rooted in
public safety: encryption makes it too difficult for investigators to access the evidence needed to catch and convict
law-breakers. Five-eyes nations have regularly published joint statements expressing their frustration with encryption
\cite{ministerial_2018} \cite{goodale_2017}. They were joined in 2020 by India and Japan in a statement emphasizing the
growing danger of \ac{CSAM} \cite{intl_2020}. Child pornography is one of the original \ac{horsemen} used to scare
people into supporting backdoors \cite{schneier_scaring_2019}, but it is also a problem growing to astonishing
proportions. A 2019 investigation by the \textit{New York Times} quoted a law officer's estimate that 400,000 New
Jerseyans, more than 4\% of the state's population, have violated child exploitation material laws
\cite{keller_internet_2019}.

@@

A significant portion of the disconnect between government and technical community representatives is disagreement over
whether law enforcement has \ii{too little} or \ii{too much} access to data. The argument for \ii{too little} is
well-represented by proponent former \ac{FBI} Director James Comey in his 2014 speech titled ``Going Dark''
\cite{comey_2014} (though he did not coin the phrase \cite{swire_encryption_2011}). The argument is presented in
\myfig{fig-arg-going-dark} including several critiques \cite{rogaway_moral_2015}.

@@

According to the "Going Dark" argument, privacy and safety are both desirable goods, but they conflict with one another;
therefore, they must be balanced. Individuals must sacrifice some of their personal good of privacy to in honor of the
public good of safety. Widespread encryption tips the scales too far towards privacy, upsetting the balance we had
before. \ac{EA} restores the balance and enables law enforcement agencies to fulfill their duty to protect the public.

@@

Most importantly, the strength of the ``Going Dark'' argument rests on law enforcement investigations failing due to
encryption. As described in \mysec{sed-arg-contrib}, there is no conclusive data regarding the extent to which
encryption is to blame for failed cases. One can certainly understand the argument, but the lack of evidence is an
issue. The highest-profile case of \ac{the-cw2}, Apple vs. FBI, ended when the \ac{FBI} broke into the phone and found
nothing of value. Tellingly, the examples cited in Comey's 2014 speech were not cases in which encryption inhibited
investigations, but were cases in which encryption \ii{could have} inhibited investigations, had it been a factor.
\cite{comey_2014}. More recently, a 2020 report titled ``Mass Extraction: The Widespread Power of U.S. Law Enforcement
to Search Mobile Phones'' revealed that law enforcement agencies currently have the upper hand on mobile device
encryption and are actually able to extract data from nearly every mobile phone on the market \cite{koepke_2020}.

Citing lack of evidence that encryption is stymieing cases only gets you so far, however. In most cases, it is
impossible to know what would have happened without the interference of strong encryption. Inability to perform
controlled tests is a characteristic of \ac{wicked-prob}. When controlled settings are unachievable, another way to
gather data is by observing naturally-occurring conditions where everything but the variable of interest is the same.
These conditions exist for encryption in messaging application ecosystem. Messaging applications WhatsApp, Facebook
Messenger, and Telegram all have large user bases have approximate feature parity. Among these services, only Facebook
Messenger does not employ \ac{E2EE}. What effect does that have on investigation? Globally, Facebook Messenger has
approximately 20\% market share as measured by active monthly users \cite{statista_2020} but accounts for 65\% of
\ac{CSAM} reports \cite{keller_internet_2019}.

@@

The ``Golden Age'' argument focuses on surveillance, its undesirability, and technology's role in it. Cryptographer
Phillip Rogaway writes at length about the negative impacts of \ac{masssurv} in his essay ``The Moral Character of
Cryptographic Work'' \cite{rogaway_moral_2015}. Rogaway asserts that ``pervasive collection \ii{itself} chills
free-speech and threatens liberal democracy.'' He argues that surveillance is fundamentally a tool of power, and for
this reason it should be resisted. Though power from the people created through representative political process is
valid, clear abuses have undercut reasonable confidence in these institutions.

@@

Another common argument is that implementing \ac{EA}---or even researching it---inexorably moves tech policy down a
slippery slope, in which government demands will never be satisfied. This argument can be used to prevent research from
those who think judicious hypothetical use of \ac{EA} tools could be positive. Going too far and too fast is certainly
dangerous, but it is both cynical and misleading to declare the permanent destruction of privacy as the inevitable end
of \ac{EA} research.

It is tempting to declare government requests for \ac{EA} disingenuous due to their hypocritical behavior towards some
of these issues. For example, if combatting \ac{CSAM} is a government priority, why has Congress underfunded the laws
they've passed, and why has the Justice Department understaffed their task force for it \cite{keller_internet_2019}?
These questions demand answers, but they do not change the validity (or invalidity) of pro-\ac{EA} arguments. The
absence of government funding does not mean technical anti-\ac{CSAM} measures are unnecessary.

The final two anti-\ac{EA} fallacies are examples of false dichotomies; they present the situation as if there are only
two outcomes. \Acp{wicked-prob} have unlimited sets of potential responses, so reducing them to two is misleading. One
false dichotomy is that the only acceptable solutions are either perfect \ac{EA} or no \ac{EA}. This leaves no room for
risk-based approaches, the typical security strategy outside the realm of cryptography. Another false dichotomy is that
regulators must either allow strong cryptography or we will live in a \ac{masssurv} dystopia. This one carries hints of
``slippery slope'' and appeal to emotion as well, framed as a choice between only two futures. Framing the situation in
all or nothing terms reduces the chance of a successful collaborative debate.

@@

Another argument used to subvert anti-EA arguments from experts goes along the lines of, since we put a man on the moon,
we can surely create secure \ac{EA} \cite{cushing_moon_2018}. This is a weak analogy. The only similarity between the
challenge of landing an astronaut on the moon and the challenge of building a cryptosystem with secure EA is that they
are difficult. Once the political commitment was made, the Apollo program solved mostly tame problems and had enormous
government backing. Resolving the encryption debate has neither of these benefits. Many similar arguments comparing
\ac{EA} to other feats of technological progress suffer the same faults.

@@

Moving on from problem framing and meritless arguments, we next turn to actions that can be taken in response to the
situation. \myfig{fig-arg-measures} divides potential solutions into the categories of current capabilities, legal
measures, and \ac{EA}. Current capabilities can be implemented today, and include maintenance of the status quo and
increasing investment in current programs. Legal measures require change the text or application of the law, but do not
require fundamentally new technical capabilities. These include compelling passwords, which requires legal
clarification, and sanctioning lawful hacking, which requires a strategic pivot and an oversight framework. (These
non-\ac{EA} approaches were first introduced in \mysec{sec-alt-approaches}.) At this level, \ac{EA} is analyzed in
general. Specific EA approaches are addressed in the next map.

@@

Each measure is considered with reference to five metrics. These metrics represent a generalization of metrics from
several sources, including two separate diverse committees gathered to analyze the encryption debate
\cite{committee_decrypting_2018} \cite{group_2019} \cite{varia_2018}. They also align closely to the four central issues
of security, safety, privacy, and trust. The five metrics used to analyze response measures are (1) minimization of
increased security risk, (2) utility to law enforcement, (3) protection of civil liberties---particularly important as
after the analysis of the ``Golden Age for Surveillance'' argument---(4) transparency, and (5) economic impact. Economic
impact is not as central an issue as the others, but it does help determine practical viability of a proposal.

@@

Compelled password disclosure is a potential solution that simply requires defendants to surrender passwords and
\acp{PIN} to their devices. Questions regarding the legality of this approach have been working their way through the
courts \cite{bittenbender_2019} \cite{sobel_2019}, as may be interpreted to conflict with the Fifth Amendment right
against self-incrimination. Even so, affordability is the strongest argument in its favor. Schneier and Kerr point out
that this approach requires the password-holder to be available to investigators, the prosecution has to overcome
several legal hurdles even if the basic approach is ruled Constitutionally legal, and even then the defendant may choose
to withhold the password and be held in contempt rather than be charged for crime evidenced by the plaintext
\cite{kerr_encryption_2017}.

\Ac{lawful-hacking} is the most prominent proposed alternative to \ac{EA}, though it is universally seen as a
sub-optimal compromise \cite{bellovin_lawful_2013} \cite{hennessey_lawful_2016} \cite{rozenshtein_wicked_2018}
\cite{kerr_encryption_2017} \cite{soesanto_2018}. One explanation for \ac{lawful-hacking}'s support is that it's a
technical route that isn't \ac{EA} itself. Another is its effectiveness against those for whom \ac{EA} would not
necessarily work. \Ac{lawful-hacking} has the advantage over \ac{EA} at being effective against organized crime and
terror groups because while they would inevitably use encryption tools to evade any \ac{EA} scheme, their operational
security would fail at some point, letting law enforcement or intelligence agencies into their networks and devices.
This approach is already in use to some extent \cite{cox_2020}, most famously to bring down cartel kingpin El Chapo
\cite{feuer_chapo_2019}.

The real change that this policy would take would be a sanctioning and formalization of this strategy. One downside is
that it would be of little use to ill-resourced departments, nullifying its usefulness for more commonplace crimes. Its
major downside is the altered relation is would create between law enforcement and tech companies. Instead of
cooperation, they are suddenly thrust into competition, with law enforcement incentivized to hoard rather than disclose
vulnerabilities it discovers. Prominent proposals suggest mandating prompt disclosure of discovered vulnerabilities
\cite{bellovin_lawful_2013} \cite{hennessey_lawful_2016}. Theoretically, the supply of vulnerabilities is very large,
and new ones could be found at a rate that maintains law enforcement access at constant levels while improving security
as a positive side effect. The government would source these vulnerabilities from a combination of the public domain,
the commercial exploit market, and a central ``Vulnerability Lab'' \cite{bellovin_lawful_2013}.

The availability and cost of exploits ebbs and flows. On one hand, January 2019 sported a \$2 million price on the
exploit market for an Apple iOS jailbreak bug \cite{goodin_zeroday_2019}. On the other hand, the October 2020 report
detailing law enforcement's mobile device cracking capabilities estimated the per-device cost to be only \$2000 a unit
\cite{koepke_2020}. As the exploit arms race continues, exploitability will be inconsistent. In the end, law enforcement
would face periods where it struggles for access, and would need to develop costly exploits in the lab. Mandatory
vulnerability disclosure is key to a \ac{lawful-hacking} proposal; however, based on the \ac{FBI}'s historical abuses of
power \cite{shamsi_2011} and Congress's distaste for funding even initiatives it has passed \cite{keller_internet_2019}
or providing strong oversight \cite{johnson_congressional_2004}, one cannot imagine that the government would actually
give up expensive vulnerabilities easily when they are the pillar of their access strategy.

The final proposal is \ac{EA} itself. Its advantage, generally speaking, is that it would provide reliable access to law
enforcement in a reliable manner. It could serve as a compliment to \ac{lawful-hacking}, blunting the incentive to hoard
vulnerabilities because it would be unnecessary for \ac{EA} compliant systems, which would presumably include mainstream
technology. In that situation, \ac{EA} would combat common crime and \ac{lawful-hacking} would combat organized crime
and terror groups. While impact on civil liberties and \ac{masssurv} depends on implementation, any proposal would be
costly to introduce and threaten U.S. product competitiveness due to perceived insecurity. Indeed, risk to security is
the largest weakness of \ac{EA}. Any proposal has to overcome significant challenges to provide acceptable levels of
risk. The next map analyzes this more closely.

@@

\myfig{fig-arg-classes} lists several classes of \ac{EA} and arguments in their favor and disfavor. Classes applicable
to both \ac{DIM} and \ac{DAR} include using weak cryptography, trusted-party key escrow, and distributed key escrow.
Using cryptographic puzzles and adding a ghost user apply to the case of \ac{DIM}, and device key escrow applies to
\ac{DAR}.

@@

It should be noted that the \ac{argmap} format works best when displaying the debate surrounding a single conclusion or
proposal. That leaves room for points and counterpoints to be elaborated in detail, as opposed to creating a tangled web
of un-elaborated connections. For the sake of brevity, this thesis considers \ac{EA}'s alternatives and variations at a
high level. For an excellent, thorough discussion of \ac{EA}'s alternatives and variations, see the National Academies
of Sciences, Engineering, and Medicine's 2018 report titled \ii{Decrypting the Encryption Debate: A Framework for
  Decision Makers} \cite{committee_decrypting_2018}.

The first \ac{EA} class is to simply use weak cryptographic ciphers or short encryption keys. This was the approach
taken before \ac{the-cw1}, when strong cryptography was not highly available and subject to export controls. No party
seriously supports this approach today, as it is irreconcilably contradictory to strong security on many levels.

Trusted-party key escrow relies on the an entity or small group of entities to store a key or key recovery information.
There are a wide variety of implementations \cite{denning_taxonomy_1996}, but by definition this class of \ac{EA}
carries a crushing weakness: the centralization of extremely sensitive information. Proponents argue that software
companies' protection of code-signing keys in hardware security modules is evidence that they can protect such sensitive
data when needed \cite{ozzie_2018}, but opponents point out that such keys are accessed quite rarely used (especially
when compared to the likely frequency of \ac{EA} requests) and yet they indeed still leak \cite{green_2018}. Once the
escrowed keys are stolen, as they inevitably would be, every device or message encrypted with them would be at risk.
This is an example of a case when the \ac{argmap} format doesn't do an argument justice---the argument against any
centralized access mechanism is extremely powerful.

Distributed key escrow differs from trusted-party in that it takes strong steps to remove centralized trust. This is
achieved by using distributed systems to make key extraction difficult and inherently public \cite{phan_key_2017}
\cite{servan_schreiber_jje_2020}. If the distributed protocols hold up, one advantage of distribution is that this
approach is that it is more likely to fail by making data unrecoverable than by making unintended data vulnerable,
though more research into this area is needed. The downside of these systems is their complexity, which could make it
costly and hard to update.

>>>>

This chapter will analyze the \ac{encryption} debate using \acp{argmap}. The maps facilitate comprehension of the
debate, but there are two important shortcomings of the maps presented here. First, argument maps should be used simply
as tools in the collaborative pursuit of the problem definition and solution. It is not a replacement for debate arising
from live discussion. Second, \acp{argmap} may deceptively portray the strength of an argument. Argument nodes do not
indicate their strength or validity. If ten unsound arguments were presented against one indisputable argument, the side
with more arguments would, regardless of their integrity, appear stronger. With those qualifications in mind, let us
begin by examining the factors at the center of the conflict.

@@

\Acl{LE} argues that encryption handcuffs its investigational capacity. The \ac{FBI} brands strong encryption as
``warrant-proof'' and states that ``the government often cannot obtain the electronic evidence necessary to investigate
and prosecute threats to public and national safety'' \cite{fbi_2020}. The pro-\ac{EA} argument is typically rooted in
public safety: encryption makes it too difficult for investigators to access the evidence needed to catch and convict
law-breakers. Five-eyes nations have regularly published joint statements expressing their frustration with encryption
\cite{ministerial_2018} \cite{goodale_2017}. They were joined in 2020 by India and Japan in a statement emphasizing the
growing danger of \ac{CSAM} \cite{intl_2020}. Child pornography is one of the original \ac{horsemen} used to scare
people into supporting backdoors \cite{schneier_scaring_2019}, but it is also a problem growing to astonishing
proportions. A 2019 investigation by the \textit{New York Times} quoted a law officer's estimate that 400,000 New
Jerseyans, more than 4\% of the state's population, have violated child exploitation material laws
\cite{keller_internet_2019}.

@@

A significant portion of the disconnect between government and technical community representatives is disagreement over
whether law enforcement has \ii{too little} or \ii{too much} access to data. The argument for \ii{too little} is
well-represented by proponent former \ac{FBI} Director James Comey in his 2014 speech titled ``Going Dark''
\cite{comey_2014} (though he did not coin the phrase \cite{swire_encryption_2011}). The argument is presented in
\myfig{fig-arg-going-dark}.

@@

According to the "Going Dark" argument, privacy and safety are both desirable goods, but they conflict with one another;
therefore, they must be balanced. Individuals must sacrifice some of their personal good of privacy to allow for the
public good of safety. Widespread encryption tips the scales too far towards privacy, upsetting the balance that existed
before. \ac{EA} restores the balance and enables law enforcement agencies to fulfill their duty to protect the public.

@@

Most importantly, the ``Going Dark'' argument relies on the premise that law enforcement investigations fail due to
encryption. As described in \mysec{sed-arg-contrib}, there is no conclusive data regarding the extent to which
encryption is to blame for failed cases. One can certainly understand the argument, but the lack of evidence is an
issue. The highest-profile case of \ac{the-cw2}, Apple vs. FBI, ended when the \ac{FBI} broke into the phone and found
nothing of value. Tellingly, the examples cited in Comey's 2014 speech were not cases in which encryption inhibited
investigations, but were cases in which encryption \ii{could have} inhibited investigations, had it been a factor.
\cite{comey_2014}. More recently, a 2020 report titled ``Mass Extraction: The Widespread Power of U.S. Law Enforcement
to Search Mobile Phones'' revealed that law enforcement agencies currently have the upper hand on mobile device
encryption and are actually able to extract data from nearly every mobile phone on the market \cite{koepke_2020}.

Citing lack of evidence that encryption is stymieing cases only gets you so far, however. In most cases, it is
impossible to know what would have happened without the interference of strong encryption. Inability to gather data from
controlled tests is a characteristic of \acp{wicked-prob}. When controlled settings are unachievable, another way to
gather data is by observing naturally-occurring conditions in which everything but the variable of interest remain are
constant. These conditions exist for encryption in messaging application ecosystem. Messaging applications WhatsApp,
Facebook Messenger, and Telegram all have large user bases and similar features. Among these services, only Facebook
Messenger does not employ \ac{E2EE}. Globally, Facebook Messenger has approximately 20\% market share as measured by
active monthly users \cite{statista_2020} but accounts for 65\% of \ac{CSAM} reports \cite{keller_internet_2019}. This
indicates that encryption does indeed affect investigations.

@@

The ``Golden Age'' argument focuses on surveillance, its undesirability, and technology's role in it. Cryptographer
Phillip Rogaway writes at length about the negative impacts of \ac{masssurv} in his essay ``The Moral Character of
Cryptographic Work'' \cite{rogaway_moral_2015}. Rogaway asserts that ``pervasive collection \ii{itself} chills
free-speech and threatens liberal democracy.'' He argues that surveillance is fundamentally a tool of power, and for
this reason it should be resisted. Though power from the people, created through representative political process, is
valid, clear abuses have undercut confidence in these institutions.

@@

Another common argument is that implementing \ac{EA}---or even researching it---inexorably moves tech policy down a
slippery slope, in which government demands will never be satisfied. This argument can be used to prevent research by
those who think judicious use of \ac{EA} tools could be positive. Going too far and too fast is certainly dangerous, but
it is both cynical and misleading to declare the permanent destruction of privacy as the inevitable end of \ac{EA}
research.

It is tempting to declare government requests for \ac{EA} disingenuous due to their hypocritical behavior towards some
of these issues. For example, if combatting \ac{CSAM} is a government priority, why has Congress underfunded the laws
it's passed, and why has the Justice Department understaffed their its task force \cite{keller_internet_2019}? These
questions demand answers, but they do not change the validity (or invalidity) of pro-\ac{EA} arguments. The absence of
government funding does not mean technical anti-\ac{CSAM} measures are unnecessary.

The final two anti-\ac{EA} fallacies are examples of false dichotomies; they present the situation as if there are only
two options. \Acp{wicked-prob} have unlimited sets of potential responses, so reducing them to two is misleading. One
false dichotomy is that the only acceptable solutions are either perfect \ac{EA} or no \ac{EA}. This leaves no room for
risk-based approaches, the typical security strategy outside the realm of cryptography. Another false dichotomy is that
regulators must either allow strong cryptography or we will live in a \ac{masssurv} dystopia. This one carries hints of
``slippery slope'' and appeal to emotion as well, framed as a choice between only two futures. Framing the situation in
all or nothing terms reduces the chance of a successful collaborative debate.

@@

Another argument used to subvert anti-EA arguments from experts goes along the lines of, since we put a man on the moon,
we can surely create secure \ac{EA} \cite{cushing_moon_2018}. This is a weak analogy. The only similarity between the
challenge of landing an astronaut on the moon and the challenge of building a cryptosystem with secure EA is that they
are difficult. Once the political commitment was made, the Apollo program solved mostly tame problems and had enormous
government backing. Resolving the encryption debate has neither of these advantages. Many similar arguments comparing
\ac{EA} to other feats of technological progress suffer the same faults.

@@

Moving on from problem framing and meritless arguments, we next turn to actions that can be taken in response to the
situation. \myfig{fig-arg-measures} divides potential solutions into the categories of current capabilities, legal
measures, and \ac{EA}. Current capabilities can be implemented today, and include maintenance of the status quo and
increasing investment in current programs. Legal measures require a change in the text or application of the law, but do
not require fundamentally new technical capabilities. These include compelling passwords, which requires legal
clarification, and sanctioning lawful hacking, which requires a strategic pivot and an oversight framework. (These
non-\ac{EA} approaches were first introduced in \mysec{sec-alt-approaches}.) At this level, \ac{EA} is analyzed in
general. Specific EA approaches are addressed in the next map.

@@

Each measure is considered according to five metrics. These metrics represent a generalization of metrics from several
sources, including two separate diverse committees gathered to analyze the encryption debate
\cite{committee_decrypting_2018} \cite{group_2019} \cite{varia_2018}. They also align closely to the four central issues
of security, safety, privacy, and trust. The five metrics used to analyze response measures are (1) minimization of
increased security risk, (2) utility to law enforcement, (3) protection of civil liberties---particularly important as
after the analysis of the ``Golden Age for Surveillance'' argument---(4) transparency, and (5) economic impact. Economic
impact is not as central an issue as the others, but it does help determine practical viability of a proposal.

@@

Compelled password disclosure is a potential solution that simply requires defendants to surrender passwords and
\acp{PIN} to their devices. Questions regarding the legality of this approach have been working their way through the
courts \cite{bittenbender_2019} \cite{sobel_2019} because of the apparent conflict with the Fifth Amendment right
against self-incrimination. Even so, affordability is the strongest argument in its favor. Schneier and Kerr point out
that this approach requires the password-holder to be available to investigators, the prosecution has to overcome
several legal hurdles even if the basic approach is ruled Constitutionally legal, and even then the defendant may choose
to withhold the password and be held in contempt rather than be charged for crime evidenced by the plaintext
\cite{kerr_encryption_2017}.

\Ac{lawful-hacking} is the most prominent proposed alternative to \ac{EA} \cite{bellovin_lawful_2013}
\cite{hennessey_lawful_2016} \cite{rozenshtein_wicked_2018} \cite{kerr_encryption_2017} \cite{soesanto_2018}.
\Ac{lawful-hacking}'s support may be due in part to the fact that it is a technical approach that isn't \ac{EA} itself.
However, its effectiveness against criminals for whom \ac{EA} would not work is its obvious benefit. This is because,
while organized crime and terror groups would still use encryption tools to evade an \ac{EA} scheme, their operational
security would fail at some point, letting law enforcement or intelligence agencies into their networks and devices.
This approach is already in use \cite{cox_2020}, most famously to bring down cartel kingpin El Chapo
\cite{feuer_chapo_2019}.

The real change that \ac{lawful-hacking} would take would be a sanctioning and formalization of this strategy.
% TODO: tie to paragraph above?

Despite its strength's \ac{lawful-hacking} is a sub-optimal compromise. Because it requires time and specialized skills,
it is unuseful for small departments and commonplace crimes. It would also alter the relationship between law
enforcement and tech companies. Law enforcement agencies would be forced into competition with tech companies if they
were incentivized to conceal the vulnerabilities they discover. Prominent proposals suggest mandating disclosure of
discovered vulnerabilities to mitigate this issue \cite{bellovin_lawful_2013} \cite{hennessey_lawful_2016}.
Theoretically, the supply of vulnerabilities is very large, so even though the disclosed vulnerabilities would be
disclosed and patched, new ones could be found at a rate that maintains law enforcement access. Government could source
these vulnerabilities from a combination of the public domain, the commercial exploit market, and a central
``Vulnerability Lab'' \cite{bellovin_lawful_2013}.

The availability and cost of exploits fluctuates. For example, in January 2019, an Apple iOS jailbreak bug was valued at
\$2 million on the exploit market \cite{goodin_zeroday_2019}. In contrast, a 2020 report revealed that cracking mobile
devices cost law enforcement a mere \$2000 per unit \cite{koepke_2020}. As the exploit arms race continues,
exploitability will be inconsistent. In the end, law enforcement would face periods where it struggles for access, and
would need to develop costly exploits in the lab. Mandatory vulnerability disclosure is necessary to avoid competition
between law enforcement and tech companies. However, based on the \ac{FBI}'s historical abuses of power
\cite{shamsi_2011} and Congress's reluctance to fund initiatives it has passed \cite{keller_internet_2019} and failure
to provide strong oversight \cite{johnson_congressional_2004}, it seems unlikely that government would readily forfeit
expensive vulnerabilities.

The final proposal is \ac{EA} itself. \ac{EA} would provide a standardized method for law enforcement to reliably access
\ac{plaintext}. It could serve as a compliment to \ac{lawful-hacking}by eliminating the incentive to conceal
vulnerabilities because it would be unnecessary for \ac{EA}-compliant systems, which would presumably include mainstream
technology. In that situation, \ac{EA} would combat common crime and \ac{lawful-hacking} would combat organized crime
and terror groups. While \ac{EA}'s impact on civil liberties and \ac{masssurv} would depend on its implementation, any
proposal would be costly to introduce and would threaten U.S. product competitiveness due to perceived insecurity. Risk
to security is the largest weakness of \ac{EA}. Any proposal must overcome significant challenges to minimize risk. The
next map analyzes this more closely.

@@

\myfig{fig-arg-classes} lists several classes of \ac{EA} and arguments in their favor and disfavor. The \ac{EA} classes
applicable to both \ac{DIM} and \ac{DAR} include weak cryptography, trusted-party key escrow, and distributed key
escrow. Using cryptographic puzzles and adding a ghost user apply to the case of \ac{DIM}, and device key escrow applies
to \ac{DAR}.

@@

% TODO: move this up? Applies to previous map as well.
It should be noted that the \ac{argmap} format works best when it displays the debate surrounding just one conclusion or
proposal. This allows adequate room for elaboration on points and counterpoints. When a map includes multiple
conclusions or proposals, it becomes a tangled web of connections, leaving no room for additional detail. For the sake
of brevity, this thesis compares several \ac{EA} variations in a single map. For an thorough discussion of \ac{EA}'s
alternatives and variations, see the National Academies of Sciences, Engineering, and Medicine's 2018 report titled
\ii{Decrypting the Encryption Debate: A Framework for Decision Makers} \cite{committee_decrypting_2018}.

The first \ac{EA} class is to simply use weak cryptographic ciphers or short encryption keys. This was the approach
taken before \ac{the-cw1}, when strong cryptography was not readily available and subjected to export controls. No party
seriously supports this approach today, as it contradicts security on many levels.

Trusted-party key escrow relies on an entity or a small group of entities to store a key or key recovery information.
There are a wide variety of implementations \cite{denning_taxonomy_1996}. This class of \ac{EA} has a crushing weakness:
it centralizes extremely sensitive information. Some argue software companies are capable of protecting such sensitive
data, citing their current practice of storing code-signing keys in hardware security modules \cite{ozzie_2018}.
However, others point out that such keys are quite rarely used (especially when compared to the likely frequency of
\ac{EA} requests), and yet they still leak \cite{green_2018}. Once the escrowed keys were stolen, as they inevitably
would be, every device or message encrypted with them would be at risk. This is an example of a case when the
\ac{argmap} format doesn't do an argument justice---the argument against any centralized access mechanism is extremely
powerful.

Distributed key escrow differs from trusted-party in that it takes strong steps to remove centralized trust. This is
achieved by using distributed systems to make key extraction difficult and publicly observable \cite{phan_key_2017}
\cite{servan_schreiber_jje_2020}. One advantage of distribution is that this approach is that it is more likely to fail
by making data unrecoverable than by making unintended data vulnerable, though more research into this area is needed.
Unfortunately, these systems would likely be costly to deploy and difficult to update due to their complexity.
